---
title: "Stock returns"
subtitle: "150 years of stock index investing"
format:
    revealjs: default
---

# Pre work {visibility="hidden"}

```{r}
library(tidyverse)
library(gt)

library(targets)

tar_source()
```

# Introduction

## TODO

TODO.

# Main point

## Step 1: How much would 1 dollar be worth today?

```{r}
tar_read(price_plot)
```

## Step 2: How much would 1 dollar be worth today? (Better represented)

```{r}
tar_read(log_price_plot)
```

## Step 3: How much would 1 dollar REALLY be worth today?

```{r}
tar_read(log_real_price_plot)
```

## Step 4: But I don't have 150 years for investing

```{r}
tar_read(rolling_real_value_plot)
```

## Step 5: Ok, but I invest monthly

```{r}
tar_read(rolling_dca_multiple_plot)
```

# Nerd info

## Nerd info 1: historical real mean return

```{r}
tar_read(log_return_plot)
```

## Nerd info 1: historical real mean return

```{r}
tar_read(risk_premium_results) |>
    gt() |>
    fmt_percent(where(is.numeric)) |>
    cols_merge(
        c(ci_lower, ci_upper),
        pattern = "[{1}, {2}]"
    ) |>
    cols_label(
        estimate = "Estimate",
        ci_lower = str_glue("Confidence interval ({scales::label_percent()(CONFIDENCE_LEVEL)})")
    ) |>
    as_raw_html()
```
